Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-07-11 article-models-ttderived.tex
added properties to extension algebras and cft-algebras

\subsection{Morphisms with extended domains}

@@

\begin{lem}
Let $\jhom{\Gamma}{{A}{P}}{B}{f}$ be a morphism and let $\jterm{\Gamma}{A}{x}$
be a term. The following three inference rules are valid
\begin{align*}
& \inference
  { \jfam{{\Gamma}{B}}{Q}
    }
  { \jfameq
      {{\Gamma}{\subst{x}{P}}}
      {\subst{x}{\jcomp{}{f}{Q}}}
      {\jcomp{}{\subst{x}{f}}{Q}}
    }
  \\
& \inference
  { \jfam{{{\Gamma}{B}}{Q}}{R}
    }
  { \jfameq
      {{{\Gamma}{\subst{x}{P}}}{\jcomp{}{\subst{x}{f}}{Q}}}
      {\subst{x}{\jcomp{}{f}{R}}}
      {\jcomp{}{\subst{x}{f}}{R}}
    }
  \\
& \inference
  { \jterm{{{\Gamma}{B}}{Q}}{R}{h}
    }
  { \jfameq
      {{{\Gamma}{\subst{x}{P}}}{\jcomp{}{\subst{x}{f}}{Q}}}
      {\jcomp{}{\subst{x}{f}}{R}}
      {\subst{x}{\jcomp{}{f}{h}}}
      {\jcomp{}{\subst{x}{f}}{h}}
    }
\end{align*}
\end{lem}

\begin{proof}
This follows from the observation in \autoref{lem:jhomdomext-jhomcodwk} 
that a morphism from
$\ctxext{A}{P}$ to $B$ in context $\Gamma$ is the same thing as a morphism
from $P$ to $\ctxwk{A}{B}$ in context $\ctxext{\Gamma}{A}$.
\end{proof}

>>>>

\subsection{Morphisms with extended domains}\label{sec:ehom}

@@

\begin{rmk}
Suppose $\jhom{\Gamma}{{A}{P}}{B}{f}$ is a morphism with an extended domain.
Then the inference rules
\begin{align*}
& \inference
  { \jterm{\Gamma}{A}{x}
    }
  { \jhom{\Gamma}{\subst{x}{P}}{B}{\subst{x}{f}}
    }
  \\
& \inference
  { \jterm{{\Gamma}{A}}{P}{y}
    }
  { \jhom{\Gamma}{A}{B}{\subst{y}{f}}
    }
\end{align*}
are valid.
This follows from the observation in \autoref{lem:jhomdomext-jhomcodwk} 
that a morphism from
$\ctxext{A}{P}$ to $B$ in context $\Gamma$ is the same thing as a morphism
from $P$ to $\ctxwk{A}{B}$ in context $\ctxext{\Gamma}{A}$.
\end{rmk}

\begin{lem}\label{lem:ehom-subst}
Let $\jhom{\Gamma}{{A}{P}}{B}{f}$ be a morphism and let $\jterm{\Gamma}{A}{x}$
be a term. The following three inference rules are valid
\begin{align*}
& \inference
  { \jfam{{\Gamma}{B}}{Q}
    }
  { \jfameq
      {{\Gamma}{\subst{x}{P}}}
      {\subst{x}{\jcomp{}{f}{Q}}}
      {\jcomp{}{\subst{x}{f}}{Q}}
    }
  \\
& \inference
  { \jfam{{{\Gamma}{B}}{Q}}{R}
    }
  { \jfameq
      {{{\Gamma}{\subst{x}{P}}}{\jcomp{}{\subst{x}{f}}{Q}}}
      {\subst{x}{\jcomp{}{f}{R}}}
      {\jcomp{}{\subst{x}{f}}{R}}
    }
  \\
& \inference
  { \jterm{{{\Gamma}{B}}{Q}}{R}{h}
    }
  { \jtermeq
      {{{\Gamma}{\subst{x}{P}}}{\jcomp{}{\subst{x}{f}}{Q}}}
      {\jcomp{}{\subst{x}{f}}{R}}
      {\subst{x}{\jcomp{}{f}{h}}}
      {\jcomp{}{\subst{x}{f}}{h}}
    }
\end{align*}
\end{lem}

\begin{proof}
Let $Q$ be a family over $\ctxext{\Gamma}{A}$.
We have the judgmental equalities
\begin{align*}
\subst{x}{\jcomp{}{f}{Q}}
& \jdeq
  \subst
    {x}
    {{f}{\ctxwk{\ctxext{A}{P}}{Q}}}
  \tag{by definition}
  \\
& \jdeq
  \subst
    { {x}{f}
      }
    { {x}
      {\ctxwk{\ctxext{A}{P}}{Q}}
      }
  \tag{by \autoref{comp-ss-f}}
  \\
& \jdeq
  \subst
    { {x}{f}
      }
    { {x}
      {\ctxwk{P}{{A}{Q}}}
      }
  \tag{by \autoref{comp-ew-f}}
  \\
& \jdeq
  \subst
    { {x}{f}
      }
    { \ctxwk
        {\subst{x}{P}}
        {\subst{x}{\ctxwk{A}{Q}}}
      }
  \tag{by \autoref{comp-sw-f}}
  \\
& \jdeq
  \subst
    { {x}{f}
      }
    { \ctxwk
        {\subst{x}{P}}
        {Q}
      }
  \tag{by \autoref{cancellation-ws-f}}
  \\
& \jdeq
  \jcomp{}{\subst{x}{f}}{Q}.
  \tag{by definition}
\end{align*}
\begin{comment}
In the case where $\xi$ is $y$ we have the judgmental equalities
\begin{align*}
\subst{y}{\jcomp{}{f}{Q}}
& \jdeq
  \subst
    { y
      }
    { {f}
      {\ctxwk{\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}{Q}}
      }
  \tag{by definition}
  \\
& \jdeq
  \subst
    { {y}{f}
      }
    { {y}
      {\ctxwk{\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}{Q}}
      }
  \tag{by \autoref{comp-ss-f}}
  \\
& \jdeq
  \subst
    { {y}{f}
      }
    { {y}
      {\ctxwk{\cftalgf{\cftalg{A}}}{{\cftalgc{\cftalg{A}}}{Q}}}
      }
  \tag{by \autoref{comp-ew-f}}
  \\
& \jdeq
  \subst
    { {y}{f}
      }
    { \ctxwk{\cftalgc{\cftalg{A}}}{Q}
      }
  \tag{by \autoref{cancellation-ws-f}}
  \\
& \jdeq
  \jcomp{}{\subst{y}{f}}{Q}.
  \tag{by definition}
\end{align*}
\end{comment}
\end{proof}

### 2014-07-11 article-models-ttinternal.tex
added properties to extension algebras and cft-algebras

@@

\begin{defn}
An \emph{extension homomorphism $\cfthom{f}$ from $\extalg{A}$ to
$\extalg{B}$ in context $\Gamma$} is a triple $\unfold{\cfthom{f}}$ consisting of
\begin{align*}
\jalign\jhom
  {\Gamma}
  {\cftalgc{\cftalg{A}}}
  {\cftalgc{\cftalg{B}}}
  {\cfthomc{\cfthom{f}}}
  \\
\jfhom*
  {\Gamma}
  {\cftalgc{\cftalg{A}}}
  {\cftalgc{\cftalg{B}}}
  {\cfthomc{\cfthom{f}}}
  {\cftalgf{\cftalg{A}}}
  {\cftalgf{\cftalg{B}}}
  {\cfthomf{\cfthom{f}}}
  \\
\jfhom*
  {\Gamma}
  {{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {{\cftalgc{\cftalg{B}}}{\cftalgf{\cftalg{B}}}}
  {\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}
  {\cftalgt{\cftalg{A}}}
  {\cftalgt{\cftalg{B}}}
  {\cfthomt{\cfthom{f}}}
\end{align*}
for which the diagrams
\begin{equation}\label{eq:exthom1}
\begin{tikzcd}
\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}
  \ar{r}{\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}
  \ar{d}[swap]{\cftctxext[\cftalg{A}]}
& \ctxext{\cftalgc{\cftalg{B}}}{\cftalgf{\cftalg{B}}}
  \ar{d}{\cftctxext[\cftalg{B}]}
  \\
\cftalgc{\cftalg{A}}
  \ar{r}[swap]{\cfthomc{\cfthom{f}}}
& \cftalgc{\cftalg{B}}
\end{tikzcd}
\end{equation}
and
\begin{equation}\label{eq:exthom2}
\begin{tikzcd}[column sep=huge]
\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}
  \ar{r}{\jvcomp{}{\cfthomf{\cfthom{f}}}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cfthomf{\cfthom{f}}}}}
  \ar{d}[swap]{\cftfamext[\cftalg{A}]}
& \jcomp{}{\cfthomc{\cfthom{f}}}{\ctxext{\cftalgf{\cftalg{B}}}{\jcomp{}{\cftctxext[\cftalg{B}]}{\cftalgf{\cftalg{B}}}}}
  \ar{d}{\jcomp{}{\cfthomc{\cfthom{f}}}{\cftfamext[\cftalg{B}]}}
  \\
\cftalgf{\cftalg{A}}
  \ar{r}[swap]{\cfthomf{\cfthom{f}}}
& \jcomp{}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{B}}}
\end{tikzcd}
\end{equation}
commute judgmentally.
\end{defn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CFT-algebras}
The notion of CFT-algebras that we will
study in this subsection will be extension algebras which also have an empty 
context $\cftempc{\cftalg{A}}$ and an empty family $\cftempf{\cftalg{A}}$ 
satisfying (among other conditions) that families over the empty context in
$\cftalg{A}$ are just the contexts of $\cftalg{A}$. We will begin with an 
auxilary lemma which will help us dealing with the internal empty contexts:

\begin{lem}\label{lem:empalg-mor}
Consider a family $\jfam{\Gamma}{A}$ with a term $\jterm{\Gamma}{A}{x}$ and 
a family $\jfam{{\Gamma}{A}}{P}$ % with a term $\jterm{{\Gamma}{A}}{P}{y}$
satisfying the judgmental equality
\begin{align}
\jalign\jfameq{\Gamma}{\subst{x}{P}}{A}
  \label{eq1:empalg-mor}
%  \\
%\jalign\jtermeq{\Gamma}{A}{\subst{x}{y}}{x}.
%  \label{eq2:empalg-mor}
\end{align}
Consider also a morphism
\begin{equation*}
\jhom{\Gamma}{{A}{P}}{B}{f}.
\end{equation*}
Then $\subst{\xi}{f}$ is a morphism from $A$ to $B$ 
in context $\Gamma$ and the following inference rules are valid for $\xi$ being 
$x$ or $y$:
\begin{align*}
& \inference
  { \jfam{{\Gamma}{B}}{Q}
    }
  { \jfameq
      {{\Gamma}{A}}
      {\subst{\xi}{\jcomp{}{f}{Q}}}
      {\jcomp{}{\subst{\xi}{f}}{Q}}
    }
  \\
& \inference
  { \jfam{{{\Gamma}{B}}{Q}}{R}
    }
  { \jfameq
      {{{\Gamma}{A}}{\jcomp{}{\subst{\xi}{f}}{Q}}}
      {\subst{\xi}{\jcomp{}{f}{R}}}
      {\jcomp{}{\subst{\xi}{f}}{R}}
    }
  \\
& \inference
  { \jterm{{{\Gamma}{B}}{Q}}{R}{h}
    }
  { \jtermeq
      {{{\Gamma}{A}}{\jcomp{}{\subst{\xi}{f}}{Q}}}
      {\jcomp{}{\subst{\xi}{f}}{R}}
      {\subst{\xi}{\jcomp{}{f}{h}}}
      {\jcomp{}{\subst{\xi}{f}}{h}}
    }
\end{align*}
\end{lem}

\begin{proof}
We only prove the first inference rule in both cases.
Let $Q$ be a family over $\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$. In the case 
where $\xi$ is $x$ we have the judgmental equalities
\begin{align*}
\subst{x}{\jcomp{}{f}{Q}}
& \jdeq
  \subst
    {x}
    {{f}{\ctxwk{\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}{Q}}}
  \tag{by definition}
  \\
& \jdeq
  \subst
    { {x}{f}
      }
    { {x}
      {\ctxwk{\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}{Q}}
      }
  \tag{by \autoref{comp-ss-f}}
  \\
& \jdeq
  \subst
    { {x}{f}
      }
    { {x}
      {\ctxwk{\cftalgf{\cftalg{A}}}{{\cftalgc{\cftalg{A}}}{Q}}}
      }
  \tag{by \autoref{comp-ew-f}}
  \\
& \jdeq
  \subst
    { {x}{f}
      }
    { \ctxwk
        {\subst{x}{\cftalgf{\cftalg{A}}}}
        {\subst{x}{\ctxwk{\cftalgc{\cftalg{A}}}{Q}}}
      }
  \tag{by \autoref{comp-sw-f}}
  \\
& \jdeq
  \subst
    { {x}{f}
      }
    { \ctxwk
        {\subst{x}{\cftalgf{\cftalg{A}}}}
        {Q}
      }
  \tag{by \autoref{cancellation-ws-f}}
  \\
& \jdeq
  \subst{{x}{f}}{\ctxwk{\cftalgc{\cftalg{A}}}{Q}}
  \tag{by \autoref{eq1:empalg-mor}}
  \\
& \jdeq
  \jcomp{}{\subst{x}{f}}{Q}.
  \tag{by definition}
\end{align*}
In the case where $\xi$ is $y$ we have the judgmental equalities
\begin{align*}
\subst{y}{\jcomp{}{f}{Q}}
& \jdeq
  \subst
    { y
      }
    { {f}
      {\ctxwk{\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}{Q}}
      }
  \tag{by definition}
  \\
& \jdeq
  \subst
    { {y}{f}
      }
    { {y}
      {\ctxwk{\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}{Q}}
      }
  \tag{by \autoref{comp-ss-f}}
  \\
& \jdeq
  \subst
    { {y}{f}
      }
    { {y}
      {\ctxwk{\cftalgf{\cftalg{A}}}{{\cftalgc{\cftalg{A}}}{Q}}}
      }
  \tag{by \autoref{comp-ew-f}}
  \\
& \jdeq
  \subst
    { {y}{f}
      }
    { \ctxwk{\cftalgc{\cftalg{A}}}{Q}
      }
  \tag{by \autoref{cancellation-ws-f}}
  \\
& \jdeq
  \jcomp{}{\subst{y}{f}}{Q}.
  \tag{by definition}
\end{align*}
\end{proof}

\begin{defn}
A \emph{CFT-algebra $\cftalg{A}$ in context $\Gamma$} is a septuple
\begin{equation*}
\unfold{\cftalg{A}}
\end{equation*}
where the quintuple $\unfold{\extalg{A}}$ is an extension
algebra in context $\Gamma$, and where
\begin{align*}
\jalign\jterm{\Gamma}{\cftalgc{\cftalg{A}}}{\cftempc{\cftalg{A}}}
  \\
\jalign\jterm{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}{\cftempf{\cftalg{A}}}
\end{align*}
which satisfy the following judgmental equalities
\begin{enumerate}
\item Families over the empty context in $\cftalg{A}$ are contexts of $\cftalg{A}$:
\begin{align}
\jalign\jfameq
  {\Gamma}
  {\subst{\cftempc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {\cftalgc{\cftalg{A}}}
  \label{empalg-eq1}
\end{align}
\item The empty family over the empty context of $\cftalg{A}$ is the empty context of $\cftalg{A}$:
\begin{align}
\jtermeq*
  {\Gamma}
  {\cftalgc{\cftalg{A}}}
  {\subst{\cftempc{\cftalg{A}}}{\cftempf{\cftalg{A}}}}
  {\cftempc{\cftalg{A}}}.
  \label{empalg-eq2}
\end{align}
\item Context extension of $\cftalg{A}$ is compatible with the empty context and
family of $\cftalg{A}$:
\begin{align}
\jtermeq*
  {{\Gamma}{\cftalgc{\cftalg{A}}}}
  {\ctxwk{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{A}}}}
  {\subst{\cftempc{\cftalg{A}}}{\cftctxext[\cftalg{A}]}}
  {\idtm{\cftalgc{\cftalg{A}}}}
  \label{cftalg-eq1}
  \\
\jtermeq*
  {{\Gamma}{\cftalgc{\cftalg{A}}}}
  {\ctxwk{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{A}}}}
  {\subst{\cftempf{\cftalg{A}}}{\cftctxext[\cftalg{A}]}}
  {\idtm{\cftalgc{\cftalg{A}}}}
  \label{cftalg-eq2}
\end{align}
\item Family extension of $\cftalg{A}$ is compatible with the empty family and the empty family
over families of $\cftalg{A}$:
\begin{align}
\jtermeq*
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {\subst{\cftempf{\cftalg{A}}}{\cftfamext}}
  {\idtm{\cftalgf{\cftalg{A}}}}
  \label{cftalg-eq3}
  \\
\jtermeq*
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {\subst{\jcomp{}{\cftctxext}{\cftempf{\cftalg{A}}}}{\cftfamext}}
  {\idtm{\cftalgf{\cftalg{A}}}}
  \label{cftalg-eq4}
\end{align}
\item Family extension over the empty context of $\cftalg{A}$ is context extension
of $\cftalg{A}$:
\begin{align}
\jhomeq*
  {\Gamma}
  {{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {\cftalgc{\cftalg{A}}}
  {\subst{\cftempc{\cftalg{A}}}{\cftfamext}}
  {\cftctxext}
  \label{cftalg-eq5}
\end{align}
\end{enumerate}
\end{defn}

\begin{rmk}\label{rmk:cftalg-defn}
We need to verify that the judgmental equalities
\autoref{cftalg-eq1,cftalg-eq2,cftalg-eq3,cftalg-eq4,cftalg-eq5}
are indeed well-typed (i.e.~compare two terms of the same type).
\begin{enumerate}
\item \autoref{lem:empalg-mor} implies that the morphisms 
$\subst{\cftempc{\cftalg{A}}}{\cftctxext}$ and
$\subst{\cftempf{\cftalg{A}}}{\cftctxext}$ both go from $\cftalgc{\cftalg{A}}$ 
to $\cftalgc{\cftalg{A}}$.
\item \label{rmkenum:famfamempf-jdeq-fam}
Now we have the judgmental equalities
\begin{align*}
\subst{\cftempf{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}
& \jdeq
  \jcomp{}{\subst{\cftempf{\cftalg{A}}}{\cftctxext}}{\cftalgf{\cftalg{A}}}
  \tag{by \autoref{lem:empalg-mor}}
  \\
& \jdeq
  \jcomp{}{\idtm{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}
  \tag{by \autoref{cftalg-eq1}}
  \\
& \jdeq
  \cftalgf{\cftalg{A}}
  \tag{by \autoref{precomp-idtm-c}}
\end{align*}
Therefore we can apply \autoref{lem:empalg-mor} with the triple
$(\cftalgf{\cftalg{A}},\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}},
\cftempf{\cftalg{A}})$ and the morphism $\cftfamext$ to see that both 
$\subst{\cftempf{\cftalg{A}}}{\cftfamext}$ and
$\subst{\jcomp{}{\cftctxext}{\cftempf{\cftalg{A}}}}{\cftfamext}$
are morphisms from $\cftalgf{\cftalg{A}}$ to $\cftalgf{\cftalg{A}}$.
\item The morphism $\subst{\cftempc{\cftalg{A}}}{\cftfamext}$ goes from
$ \subst
    {\cftempc{\cftalg{A}}}
    {\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}}
  $
to $\subst{\cftempc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}$. For the domain we
have the judgmental equalities
\begin{align*}
  \subst
    {\cftempc{\cftalg{A}}}
    {\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}}
& \jdeq
  \ctxext
    {\subst{\cftempc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
    {\subst{\cftempc{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}}
  \tag{by \autoref{comp-se-c}}
  \\
& \jdeq
  \ctxext
    {\cftalgc{\cftalg{A}}}
    {\subst{\cftempc{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}}
  \tag{by \autoref{empalg-eq1}}
  \\
& \jdeq
  \ctxext
    {\cftalgc{\cftalg{A}}}
    {\cftalgf{\cftalg{A}}}
  \tag{by \autoref{rmkenum:famfamempf-jdeq-fam} above}
\end{align*}
The codomain of $\subst{\cftempc{\cftalg{A}}}{\cftfamext}$
is judgmentally equal to $\cftalgc{\cftalg{A}}$ by
\autoref{empalg-eq1}.
\end{enumerate}
\end{rmk}

>>>>

\begin{lem}
Let $\extalg{Q}$ be an extension algebra in context $\ctxext{\Gamma}{B}$ and let
$\jfam{\Gamma}{A}$. Then we have the judgmental equality
\begin{equation*}
\ctxwk{A}{\extalg{F_Q}}\jdeq\extalg{F}_{\ctxwk{A}{\extalg{Q}}}
\end{equation*}
of extension algebras in context $\ctxext{{\Gamma}{A}}{\ctxwk{A}{B}}$.
\end{lem}

\begin{lem}
Let $\extalg{Q}$ be an extension algebra in context $\ctxext{{\Gamma}{A}}{P}$ 
and let $\jterm{\Gamma}{A}{x}$. Then we have the judgmental equality
\begin{equation*}
\subst{x}{\extalg{F_Q}}\jdeq\extalg{F}_{\subst{x}{\extalg{Q}}}
\end{equation*}
of extension algebras in context $\ctxext{\Gamma}{\subst{x}{P}}$.
\end{lem}

@@

\begin{defn}
An \emph{extension homomorphism $\cfthom{f}$ from $\extalg{A}$ to
$\extalg{B}$ in context $\Gamma$} is a triple $\unfold{\cfthom{f}}$ consisting of
\begin{align*}
\jalign\jhom
  {\Gamma}
  {\cftalgc{\cftalg{A}}}
  {\cftalgc{\cftalg{B}}}
  {\cfthomc{\cfthom{f}}}
  \\
\jalign\jfhom
  {\Gamma}
  {\cftalgc{\cftalg{A}}}
  {\cftalgc{\cftalg{B}}}
  {\cfthomc{\cfthom{f}}}
  {\cftalgf{\cftalg{A}}}
  {\cftalgf{\cftalg{B}}}
  {\cfthomf{\cfthom{f}}}
  \\
\jalign\jfhom
  {\Gamma}
  {{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {{\cftalgc{\cftalg{B}}}{\cftalgf{\cftalg{B}}}}
  {\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}
  {\cftalgt{\cftalg{A}}}
  {\cftalgt{\cftalg{B}}}
  {\cfthomt{\cfthom{f}}}
\end{align*}
for which the diagrams
\begin{equation}\label{eq:exthom1}
\begin{tikzcd}
\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}
  \ar{r}{\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}
  \ar{d}[swap]{\cftctxext[\cftalg{A}]}
& \ctxext{\cftalgc{\cftalg{B}}}{\cftalgf{\cftalg{B}}}
  \ar{d}{\cftctxext[\cftalg{B}]}
  \\
\cftalgc{\cftalg{A}}
  \ar{r}[swap]{\cfthomc{\cfthom{f}}}
& \cftalgc{\cftalg{B}}
\end{tikzcd}
\end{equation}
and
\begin{equation}\label{eq:exthom2}
\begin{tikzcd}[column sep=huge]
\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}
  \ar{r}{\jvcomp{}{\cfthomf{\cfthom{f}}}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cfthomf{\cfthom{f}}}}}
  \ar{d}[swap]{\cftfamext[\cftalg{A}]}
& \jcomp{}{\cfthomc{\cfthom{f}}}{\ctxext{\cftalgf{\cftalg{B}}}{\jcomp{}{\cftctxext[\cftalg{B}]}{\cftalgf{\cftalg{B}}}}}
  \ar{d}{\jcomp{}{\cfthomc{\cfthom{f}}}{\cftfamext[\cftalg{B}]}}
  \\
\cftalgf{\cftalg{A}}
  \ar{r}[swap]{\cfthomf{\cfthom{f}}}
& \jcomp{}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{B}}}
\end{tikzcd}
\end{equation}
commute judgmentally.
\end{defn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CFT-algebras}
The notion of CFT-algebras that we will
study in this subsection will be extension algebras which also have an empty 
context $\cftempc{\cftalg{A}}$ and an empty family $\cftempf{\cftalg{A}}$ 
satisfying (among other conditions) that families over the empty context in
$\cftalg{A}$ are just the contexts of $\cftalg{A}$.

\begin{defn}
A \emph{CFT-algebra $\cftalg{A}$ in context $\Gamma$} is a septuple
\begin{equation*}
\unfold{\cftalg{A}}
\end{equation*}
where the quintuple $\unfold{\extalg{A}}$ is an extension
algebra in context $\Gamma$, and where
\begin{align*}
\jalign\jterm{\Gamma}{\cftalgc{\cftalg{A}}}{\cftempc{\cftalg{A}}}
  \\
\jalign\jterm{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}{\cftempf{\cftalg{A}}}
\end{align*}
which satisfy the following judgmental equalities
\begin{enumerate}
\item Families over the empty context in $\cftalg{A}$ are contexts of $\cftalg{A}$:
\begin{align}
\jalign\jfameq
  {\Gamma}
  {\subst{\cftempc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {\cftalgc{\cftalg{A}}}
  \label{empalg-eq1}
\end{align}
\item The empty family over the empty context of $\cftalg{A}$ is the empty context of $\cftalg{A}$:
\begin{align}
\jalign\jtermeq
  {\Gamma}
  {\cftalgc{\cftalg{A}}}
  {\subst{\cftempc{\cftalg{A}}}{\cftempf{\cftalg{A}}}}
  {\cftempc{\cftalg{A}}}.
  \label{empalg-eq2}
\end{align}
\item Context extension of $\cftalg{A}$ is compatible with the empty context and
family of $\cftalg{A}$:
\begin{align}
\jalign\jtermeq
  {{\Gamma}{\cftalgc{\cftalg{A}}}}
  {\ctxwk{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{A}}}}
  {\subst{\cftempc{\cftalg{A}}}{\cftctxext[\cftalg{A}]}}
  {\idtm{\cftalgc{\cftalg{A}}}}
  \label{cftalg-eq1}
  \\
\jalign\jtermeq
  {{\Gamma}{\cftalgc{\cftalg{A}}}}
  {\ctxwk{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{A}}}}
  {\subst{\cftempf{\cftalg{A}}}{\cftctxext[\cftalg{A}]}}
  {\idtm{\cftalgc{\cftalg{A}}}}
  \label{cftalg-eq2}
\end{align}
\item Family extension of $\cftalg{A}$ is compatible with the empty family and the empty family
over families of $\cftalg{A}$:
\begin{align}
\jalign\jtermeq
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {\subst{\cftempf{\cftalg{A}}}{\cftfamext}}
  {\idtm{\cftalgf{\cftalg{A}}}}
  \label{cftalg-eq3}
  \\
\jalign\jtermeq
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {\subst{\jcomp{}{\cftctxext}{\cftempf{\cftalg{A}}}}{\cftfamext}}
  {\idtm{\cftalgf{\cftalg{A}}}}
  \label{cftalg-eq4}
\end{align}
\item Family extension over the empty context of $\cftalg{A}$ is context extension
of $\cftalg{A}$:
\begin{align}
\jalign\jhomeq
  {\Gamma}
  {{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {\cftalgc{\cftalg{A}}}
  {\subst{\cftempc{\cftalg{A}}}{\cftfamext}}
  {\cftctxext}
  \label{cftalg-eq5}
\end{align}
\end{enumerate}
\end{defn}

\begin{rmk}\label{rmk:cftalg-defn}
We need to verify that the judgmental equalities
\autoref{cftalg-eq1,cftalg-eq2,cftalg-eq3,cftalg-eq4,cftalg-eq5}
are indeed well-typed (i.e.~compare two terms of the same type).
\begin{enumerate}
\item \autoref{lem:ehom-subst} implies that the morphisms 
$\subst{\cftempc{\cftalg{A}}}{\cftctxext}$ and
$\subst{\cftempf{\cftalg{A}}}{\cftctxext}$ both go from $\cftalgc{\cftalg{A}}$ 
to $\cftalgc{\cftalg{A}}$.
\item \label{rmkenum:famfamempf-jdeq-fam}
Now we have the judgmental equalities
\begin{align*}
\subst{\cftempf{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}
& \jdeq
  \jcomp{}{\subst{\cftempf{\cftalg{A}}}{\cftctxext}}{\cftalgf{\cftalg{A}}}
  \tag{by \autoref{lem:ehom-subst}}
  \\
& \jdeq
  \jcomp{}{\idtm{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}
  \tag{by \autoref{cftalg-eq1}}
  \\
& \jdeq
  \cftalgf{\cftalg{A}}
  \tag{by \autoref{precomp-idtm-c}}
\end{align*}
Therefore we can apply \autoref{lem:ehom-subst} with the triple
$(\cftalgf{\cftalg{A}},\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}},
\cftempf{\cftalg{A}})$ and the morphism $\cftfamext$ to see that both 
$\subst{\cftempf{\cftalg{A}}}{\cftfamext}$ and
$\subst{\jcomp{}{\cftctxext}{\cftempf{\cftalg{A}}}}{\cftfamext}$
are morphisms from $\cftalgf{\cftalg{A}}$ to $\cftalgf{\cftalg{A}}$.
\item The morphism $\subst{\cftempc{\cftalg{A}}}{\cftfamext}$ goes from
$ \subst
    {\cftempc{\cftalg{A}}}
    {\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}}
  $
to $\subst{\cftempc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}$. For the domain we
have the judgmental equalities
\begin{align*}
  \subst
    {\cftempc{\cftalg{A}}}
    {\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}}
& \jdeq
  \ctxext
    {\subst{\cftempc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
    {\subst{\cftempc{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}}
  \tag{by \autoref{comp-se-c}}
  \\
& \jdeq
  \ctxext
    {\cftalgc{\cftalg{A}}}
    {\subst{\cftempc{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}}}}
  \tag{by \autoref{empalg-eq1}}
  \\
& \jdeq
  \ctxext
    {\cftalgc{\cftalg{A}}}
    {\cftalgf{\cftalg{A}}}
  \tag{by \autoref{rmkenum:famfamempf-jdeq-fam} above}
\end{align*}
The codomain of $\subst{\cftempc{\cftalg{A}}}{\cftfamext}$
is judgmentally equal to $\cftalgc{\cftalg{A}}$ by
\autoref{empalg-eq1}.
\end{enumerate}
\end{rmk}
